A word-sense representation for documents based on information value and word sense disambiguation

### 2014-04-01 paper/refactor.tex
Rewrite abstract (well, just correcting it)

\begin{article}
\begin{abstract}
In this project we analyzed some Lenin works in order to identify the presence of some well known topics of his biography. To achieve this, we defined and implemented a simple distance metric between a word-sense and a document and confronted this metric using a evaluation set of word-senses against a reduced set of  documents with well known topics. During this work, we generated an indexed database of Lenin's complete works from a web site\cite{LENIN} and we applied a serie of well known syntactic, semantic and lexicographic tools in order to model the similarity between a document and a word-sense. We applied information value\cite{DARWIN} and a simple algorithm of word sense disambiguation\cite{LESK} based on wordnet\cite{WORDNET} in order to generate the \textit{top senses} (or principal senses) of a document. We compare this \textit{top senses} for some documents of well known topics agains some senses of interest (for example: revolution, war, government) and observed the shape of the results. 
\end{abstract}

>>>>

\begin{article}
\begin{abstract}
In this project we analyzed some Lenin works in order to identify the presence of some topics of his biography. To achieve this, we defined and implemented a simple metric distance between a word-sense and a document and confronted this metric using a evaluation set of word-senses against a reduced set of  documents with well known topics. During this work, we generated an indexed database of Lenin's complete works from a web site\cite{LENIN} and we applied a series of syntactic, semantic and lexicographic tools in order to model the similarity between a document and a word-sense. We applied information value\cite{DARWIN} and a simple algorithm of word sense disambiguation\cite{LESK} based on Wordnet\cite{WORDNET} in order to generate the \emph{top senses} (or principal senses) of a document. Finally, we compare them against some semantic senses of interest (for example: revolution, war, philosophy, etc). 
\end{abstract}
